Multireference alignment meets blind deconvolution

### 2017-11-16 TEX/draft2.tex
Some updates in the code and the TEX

\section{Conclusion} \label{sec:conclusion}

>>>>

We use the definition of signal--to--noise ratio ($\SNR$) as
\begin{equation}
\SNR = \frac{\|y_c\|_2^2}{\|y_c-y\|_2^2},
\end{equation}
where $y_c$ is the measurement before adding the noise. The error is measured as 
\begin{equation}
\textrm{error}  = \frac{\|\hat{x}-x\|}{\|x\|}.
\end{equation}

A representative example is given in Figure ?

An experiment for constant noise level $\sigma=1$ and varying $k$ appears in Figure~\ref{fig:varyingK}. The error stops decreasing at some level from obvious reasons.

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{errXP1.pdf}
	\caption{\label{fig:varyingK}The recovery error as a function of $k$, the number of signal appearances (approximately!) for $\sigma=1$. We worked with i.i.d.\ signal of length $L=1$ (same signal for all experiments), the window size was chosen as $W=10L$ and the number of measurements was chosen as $N =6Wk $. In average, $1/\SNR\approx 30$.}
\end{figure}
\section{Conclusion} \label{sec:conclusion}
Here we conclude the paper
